\Large \bf Lissy: Experimenting with on-chain order books

### 2022-06-03 LaTeX-LNCS-2022/sections/paper.tex
removed anon GitHub link -- finalized

% EDITS TO BE MADE:
% 1- Different market participants would have different preference about various markets. Which one is best for which? Jeremy in proposal: could be a chart
% 2- Add a subsection on latency
% 3- For enqueue and dequeue performance tests, justify why you picked 50 integers

@@

There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).

Conventional financial markets (\eg NYSE, NASDAQ) use both continuous time trading during open hours, and a call market before and during open hours to establish an opening price and a closing price. After early experiments at implementing continuous time trading on Ethereum (\eg EtherDelta, OasisDEX), it was generally accepted that conventional trading is infeasible on Ethereum for performance reasons. Centralized exchanges continued their predominance, while slowly some exchanges moved partial functionality on-chain (\eg custody of assets) while executing trades off-chain.

>>>>

@@

There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction). 
fa
Conventional financial markets (\eg NYSE, NASDAQ) use both continuous time trading during open hours, and a call market before and during open hours to establish an opening price and a closing price. After early experiments at implementing continuous time trading on Ethereum (\eg EtherDelta, OasisDEX), it was generally accepted that conventional trading is infeasible on Ethereum for performance reasons. Centralized exchanges continued their predominance, while slowly some exchanges moved partial functionality on-chain (\eg custody of assets) while executing trades off-chain.
